\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Typo fix.
Proofread \label{states}.

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}. E\# and $\mbox{e\#}^\prime$ are equivalent, but $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\

\noindent success states: 
\begin{itemize}
\item s0: no bridge no proxy
\item s1: valid bridge, no proxy
\item s2: valid bridge and valid proxy (blank port)
\item s3: valid bridge and valid proxy (specified port)
\end{itemize}

@@

Same inputs can lead to different end states. Tor Launcher will connect to a proxy successfully with the port left blank if the proxy uses port 80 (s2) but will not if the proxy uses another port (e12).

@@

\begin{enumerate}
\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
\item{I am able to provide my own transportation to the University of California, Berkeley 
campus.}
\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
\item{What is your gender?}
\item{What is your age?}
\item{Please select your highest completed (or current) level of education.}
\item{What is your occupation?} 
\item{Do you speak any languages other than English fluently?}
\item{If you have a personal computer, what kind do you use?}
\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
\item{How often do you use the following software or features? \textit{<answer choices: a grid of radio buttons. Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption. Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
\end{enumerate}
Thank you for filling out this form. You are now done!

@@

\section{Qualitative Testing Observations}
\label{summary}
We summarize of each participant's session.

>>>>

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
Here we define the end state codes that appear in Figure~\ref{fig:digraph}.
e\# and $\mbox{e\#}^\prime$ are equivalent, except that $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\

\noindent success states: 
\begin{itemize}
\item s0: no bridge, no proxy
\item s1: valid bridge, no proxy
\item s2: valid bridge and valid proxy (blank port)
\item s3: valid bridge and valid proxy (specified port)
\end{itemize}

@@

The same inputs can lead to different end states,
depending on the network environment.
For example, Tor Launcher will connect to a proxy successfully with the port left blank if the proxy uses port 80 (s2) but will not if the proxy uses another port (e12).

@@

\begin{enumerate}
\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
\item{I am able to provide my own transportation to the University of California, Berkeley 
campus.}
\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
\item{What is your gender?}
\item{What is your age?}
\item{Please select your highest completed (or current) level of education.}
\item{What is your occupation?} 
\item{Do you speak any languages other than English fluently?}
\item{If you have a personal computer, what kind do you use?}
\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
\item{How often do you use the following software or features? \textit{<answer choices: a grid of radio buttons. Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption. Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
\end{enumerate}
Thank you for filling out this form. You are now done!

@@

\section{Qualitative Testing Observations}
\label{summary}
We summarize each participant's session.
